Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-22 Paper2015.tex
Clarified some discussion in response to comments from AVP.

Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations and TOF measurements~\cite{Prokofiev2009,Prokofiev2014}.
The SUP data are also compared with results from Geant4 simulations of the bare target~\cite{Platt2013}.
These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasise the shape of the spectra rather than their integral fluence rate.
%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
The present results show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement between the present results and the analytical fit from~\cite{Prokofiev2014} (which cannot reproduce the structure in the evaporation peak around \SI{1}{\MeV}).

>>>>

Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations and TOF measurements~\cite{Prokofiev2009,Prokofiev2014}.
The SUP data are also compared with results from Geant4 simulations of the bare target~\cite{Platt2013}.
These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasise the shape of the spectra rather than their integral fluence rate.
%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
At SUP, the present results show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
Fig.~\ref{fig:LethargyplotCUP} shows good agreement between the present results and the analytical fit from~\cite{Prokofiev2014}, especially in the evaporation peak around \SI{1}{\MeV} (the fit cannot reproduce the structure in this energy region).
